---
title: "Step 2 Prioritization Data Summary and Output"
author: "Ryan Niemeyer, UCSRB"
date: "Last Edited: `r format(Sys.time(), '%B %d, %Y')` "
output: html_document
  # pdf_document:
  # toc: true
  #  toc_depth: 2
---

Markdown cheat sheet: https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet



<!-- regular html comment --> 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data, include = FALSE}
library(readr)
library(dplyr)
library(readxl)

# ----- for mapping ---
library(ggplot2)
library(ggmap)
library(maps)
library(mapdata)

# !!!!! HERE read in the data you want to print (e.g. Habitat_Attribute_Scores, Reach_Info, etc.)
# !!!!! probably jsut want to read in the MASTER
```

```{r Read in Data from MAster, include=FALSE}
# -------------- MASTER path and file ----------
folder_x = "Y:/UCRTT/Prioritization/Step 2/Habitat Evaluation/"
master_file = "MASTER_Step2_REVIEWDRAFT_071321.xlsx"
MASTER_Data_path = paste(folder_x,master_file, sep="")   # Data from Okanogan EDT results
Habitat_Quality_Scores_MASTER = read_excel( MASTER_Data_path , sheet="Habitat Quality Pathway", skip=1)

# ----------------- Read in Shapefiles ---------------
# ------ updated with Okanogan EDT data layers -----------------
reaches_path = "Y:/UCRTT/Prioritization/Step 2/Data/GIS/Reaches/Reaches.shp"
reaches <- sf::st_read(reaches_path) # this shapefile does not show up properly
reaches <- sf::st_transform(reaches, 4326)

```



```{r Function for categorical output and color, include=FALSE}

# -------------- FUNCTION to generate category and color from REI score (1,3,5) ----------
REI_category_fxn = function(score_x){
  if(score_x == 1){
    category_x = "Unacceptable"
    color_x = "red"
  }else if(score_x > 3){
    category_x = "Adequate"
    color_x = "forestgreen"
  }else{
    category_x = "At Risk"
    color_x = "gold"
  }
  
  output_x = c(category_x, color_x)
  return(output_x)
}



# ---------- FUNCTION to generate color from a variable --------
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}

# ----- Function to pull REI score/category/color based on A) ReachName and B) habitat attribute -----

Habitat_Quality_REI_metric_FUNCTION = function(ReachName_x, Habitat_Attribute_x){
  
  habitat_attribute_row_x <- Habitat_Quality_Scores_MASTER %>%
    filter(ReachName == ReachName_x) 
  
  habitat_attribute_numeric_output = habitat_attribute_row_x[1,Habitat_Attribute_x]
  
  # ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
  category_output_x = REI_category_fxn(habitat_attribute_numeric_output)
  category_x = category_output_x[1]
  color_x = category_output_x[2]
  output_x = c(habitat_attribute_numeric_output, category_x, color_x)
  
  # ---------- if score is not present ----------
  if( habitat_attribute_numeric_output == "NA" ){
    output_x = c("NA", "not present", "black")
  }
  return(output_x)
  
}



```


## Prioritization Overview

This is the R Code for the Step 2 of the [UCSRB Habitat Prioritization process](https://www.ucsrb.org/prioritization/). I will endeavor to update the data available on this page, however the most up-to-date results for Step 2 can be found on the Prioritization Products Page. For each script, the last update is listed on the right (e.g. "2 months ago").

## Reach and Action Proiritizatoin

The RTT decided to use three pathways to develop prioritized reaches and actions: Habitat Quality pathway, Limiting Factors pathway, and fish passage pathway. This python tool deals primarily with the Habitat Quality and Limiting Factors pathway, and the fish passage pathways are uploaded to the action categories manually. The filters and criteria for filters (as of October 14th, 2020) are overview in this [google slides presentation](https://docs.google.com/presentation/d/1dEJ-A_LlW1HkxfIjOfLmjRxS1DRR_nWGOsBlZj5khss/edit?usp=sharing).

# Individual Reach Summaries

for(reach_name_x in Habitat_Quality_Scores_MASTER$ReachName[c(100,200,220,300,400)]){


}
```{r Reach Name, echo=FALSE}
reach_name_x = "Entiat River Lake 01"
```

<h1 style="font-size:40px;">`r colorize(reach_name_x, "blue")`</h1>  

```{r Map Reach, echo=FALSE}

# -------- pull reach row -------
reach_x_i =  which(reaches$ReachName == reach_name_x )
df_x = as.data.frame( reaches$geometry[[reach_x_i]][[1]] )
colnames(df_x) = c("lon", "lat")

downloaded_map <- get_map(location = c(lon = mean(df_x$lon), lat = mean(df_x$lat)), maptype = "satellite", source = "google", zoom = 15)

ggmap(downloaded_map) + 
  geom_path(data = df_x, color="firebrick1", size = 2, lineend = "round") 

```

### Coarse Substrate 
```{r Coarse Substrate, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Coarse Substrate")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Coarse Substrate** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Cover- Wood 
```{r Cover- Wood, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Cover- Wood")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Cover- Wood** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Channel Stability
```{r Channel Stability, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Channel Stability")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Channel Stability** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Bank Stability
```{r Bank Stability, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Bank Stability")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Bank Stability** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Stability (average of Channel Stability and Bank Stability)
```{r Stability, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Stability")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Stability** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Pool Quantity and Quality
```{r Pool Quantity and Quality, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Pool Quantity & Quality")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Pool Quantity & Quality** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Floodplain Connectivity
```{r Floodplain Connectivity, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Floodplain Connectivity")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Floodplain Connectivity** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Off-Channel/Side-Channels
```{r Off-Channel/Side-Channels, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Off-Channel/Side-Channels")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Off-Channel/Side-Channels** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Riparian-Disturbance
```{r Riparian-Disturbance, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Riparian-Disturbance")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Riparian-Disturbance** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Riparian- Canopy Cover
```{r Riparian- Canopy Cover, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Riparian- Canopy Cover")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Riparian- Canopy Cover** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Riparian (average of RIparian-Disturbance and Riparian- Canopy Cover)
```{r Riparian, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Riparian")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Riparian** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Flow- Summer Base Flow
```{r Flow- Summer Base Flow, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Flow- Summer Base Flow")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Flow- Summer Base Flow** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### Temperature- Rearing
```{r Temperature- Rearing, echo=FALSE}
# ----------- generate category (Unacceptable, At Risk, Adequate), color (red, yellow, green) -----
output_x = Habitat_Quality_REI_metric_FUNCTION(reach_name_x, "Temperature- Rearing")
REI_number_x = output_x[1]
REI_category_x = output_x[2]
REI_color_x = output_x[3]
```

The **Temperature- Rearing** rating is **`r colorize(REI_category_x, REI_color_x)`** or  **`r colorize(REI_number_x, REI_color_x)`**.

### End of code


