---
title: "Step 2 Prioritization Data Summary and Output"
output:
  pdf_document:
    toc: true
    toc_depth: 2
author: Ryan Niemeyer, UCSRB
---

Markdown cheat sheet: https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prioritization Overview

This is the R Code for the Step 2 of the [UCSRB Habitat Prioritization process](https://www.ucsrb.org/prioritization/). I will endeavor to update the data available on this page, however the most up-to-date results for Step 2 can be found on the Prioritization Products Page. For each script, the last update is listed on the right (e.g. "2 months ago").

## Reach and Action Proiritizatoin

The RTT decided to use three pathways to develop prioritized reaches and actions: Habitat Quality pathway, Limiting Factors pathway, and fish passage pathway. This python tool deals primarily with the Habitat Quality and Limiting Factors pathway, and the fish passage pathways are uploaded to the action categories manually. The filters and criteria for filters (as of October 14th, 2020) are overview in this [google slides presentation](https://docs.google.com/presentation/d/1dEJ-A_LlW1HkxfIjOfLmjRxS1DRR_nWGOsBlZj5khss/edit?usp=sharing).


## Data Overview

(INCLUDE code that outputs the data)

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

