---
title: "Step 2 Prioritization Data Summary and Output"
output: html_document
author: Ryan Niemeyer, UCSRB
---

Markdown cheat sheet: https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prioritization Overview

This is the R Code for the Step 2 of the [UCSRB Habitat Prioritization process](https://www.ucsrb.org/prioritization/). I will endeavor to update the data available on this page, however the most up-to-date results for Step 2 can be found on the Prioritization Products Page. For each script, the last update is listed on the right (e.g. "2 months ago").

## R Code Overview




## Data Overview

(INCLUDE code that outputs the data)

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

